---
name: Nathaniel Price
docname: "CV"
fontawesome: yes
address: "Macomb, Michigan"
phone: "+1 (586) 915 7434"
email: "hartli@mail.gvsu.edu"
www: ""
date: "`r format(Sys.time(), '%B %Y')`"
output: function(...) {source('hart_entries.R');vitae:::set_entry_formats(hart_entries);vitae::cv_document(..., template = "CVtemplate.tex", citation_package = "biblatex")}
---

```{r setup, include=FALSE}
# To save log files
# rmarkdown::render("LiamHartWebsite/CV.Rmd", clean = FALSE)

knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE)

library(tidyverse)
library(vitae)
library(lubridate)
library(glue)
library(rlang)
```

```{r loadData}

# Education
education <- data.table::fread(here::here("data/education.csv"),
                               encoding = "UTF-8") %>%
  as_tibble() %>%
  mutate(
    begin = as.Date(begin, format = "%m/%d/%y"),
    end = as.Date(end, format = "%m/%d/%y")
  )

# Grants, Honors & Scholarships
awards <- data.table::fread(here::here("data/grants_honors_scholarships.csv"),
                            encoding = "UTF-8") %>%
  as_tibble()

# Research titles



# Research descriptions


# Job titles
job.titles <- data.table::fread(here::here("data/job_titles.csv"),
                                encoding = "UTF-8") %>%
  as_tibble() %>%
  mutate(
    begin = as.Date(begin, format = "%m/%d/%y"),
    end = as.Date(end, format = "%m/%d/%y")
  )


# Job descriptions
job.descriptions <-
  data.table::fread(here::here("data/job_descriptions.csv"),
                    encoding = "UTF-8") %>%
  as_tibble()

# Campus Involvement


# Professional Affiliations

```








<p align="center">**Liam W. Hart**</p>
<p align="center">Curriculum Vitae</p>
<p align="center">18115 Denali Dr</p>
<p align="center">Macomb, MI 48042</p>
<p align="center">\(586\) 915-7434</p>
<p align="center">hartli@mail.gvsu.edu</p>

**Liam W. Hart**
Curriculum Vitae
18115 Denali Dr
Macomb, MI 48042
(586) 915-7434 hartli@mail.gvsu.edu

**EDUCATION**

2021 B.S., Psychology

Grand Valley State University

Major: Psychology

Minor: Applied Statistics

> Honors Project: Perspectives on Psilocybin: The Science and Mysticism of Magic Mushrooms (Podcast)

Supervisor: Professor Roger Gilles

GPA: 3.719

**GRANTS, HONORS, & SCHOLARSHIPS**

2022 Psi Chi Regional Conference Travel Grant

2022 Office of Undergraduate Research Conference Travel Grant, Grand Valley State University

2022 Excellence-in-a-Discipline Award, Grand Valley State University

2022 Robert Hendersen Leadership Award, Grand Valley State University

2022 Outstanding Creative Achievement, Grand Valley State University Frederik Meijer Honors College. Project: "Perspectives on Psilocybin: The Science and Mysticism of Magic Mushrooms."

2021 Undergraduate Research Scholar, Grand Valley State University

2021 Student Summer Scholar, Office of Undergraduate Research, Grand Valley State University. Project: "Information About Past Beliefs Influences Current Beliefs."

2021 Grand Finish Grant, Grand Valley State University

2019-2021 Dean's List, Grand Valley State University

2018-2021 Award for Excellence, Grand Valley State University

2018-2021 Faculty Scholarship, Grand Valley State University

**RESEARCH EXPERIENCE**

**Research Assistant**

*Department of Psychology*

Grand Valley State University

2020-Present

**Responsibilities:**

> I assisted Drs. Michael Wolfe and Todd Williams in their research on the nature of beliefs and interplay with argumentative discourse. Responsibilities included survey creation, data preparation, data analysis, data visualization, hand-coding essays, and the dissemination of research findings.

**Research Assistant**

*Department of Psychology*

Grand Valley State University

2019-Present

**Responsibilities:**

> I worked under the supervision of Dr. Jing Chen to design and conduct a study examining the effectiveness of mindfulness meditation in reducing anxiety and depression among an aging population. We obtained IRB approval, however the pandemic brought this project to an early end. After, I worked with Dr. Chen to write a manuscript and present data on the effectiveness of service-learning built in a lecture-based aging course in reducing ageism.

**Research Assistant**

*Department of Movement Science*

Grand Valley State University

2018-2019

**Responsibilities:**

> I assisted Dr. Stephen Glass and his other research assistants in measuring the muscle activation in exercising with various instruments, such as fiberglass resistance poles and a water-filled instability tube. I aided in the writing of IRB submissions and facilitated the experimental sessions.

**TEACHING EXPERIENCE**

**Mentor**

Psych Friends Peer Mentoring Program

Grand Valley State University

2021

**Responsibilities:**

> I mentored undergraduate psychology students in their courses in psychology and statistics, and provided general mentorship as a senior student. This position required a sound background in academics and an understanding of effective studying techniques. Additionally, I focused on helping younger psychology students understand the importance of research methods and reading academic papers for graduate school.

**WORK EXPERIENCE**

**Climbing Instructor**

Planet Rock

2022-Present

**Responsibilities:**

> I taught climbers how to climb and belay on top-rope and lead safely and efficiently. This position required proficient knowledge about safe practices in climbing and the relevant gear. I firmly believe that the teaching aspect of this job will transfer well into any position that involves teaching or presenting information.

**CAMPUS INVOLVEMENT**

2022 Panelist: Undergraduate Research Fair, Allendale, MI; Grand Valley State University

2021 President, Grand Valley State University Psi Chi Chapter

**PAPERS IN PROGRESS**

Hart, L. Wolfe, M., Russel, G., Williams, T. (in progress). Belief Change After Reading Predicts Argumentative Essay Content

Chen, J., Hart, L. (in progress). Can Ageism Be Reduced by Service Learning Built in a Lecture-Based Aging Course?

**CONFERENCE PRESENTATIONS**

Hart, L., Russel, G., Wolfe, M., & Williams, T. (2022) Belief Change After Reading Predicts Argumentative Essay Content. Paper presented at Society for Text and Discourse, virtual.

Hart, L., Russel, G., Wolfe, M., & Williams, T. (2022) Information About Past Beliefs Influences Current Beliefs. Poster presented at Midwestern Psychological Association Conference, Chicago, IL.

Hart, L. (2021) Information about Past Beliefs Influences Current Beliefs. Paper presented at the Grand Valley State University Student Summer Scholars Showcase, Allendale, MI.

Hart, L. (2021) Can Ageism Be Reduced by Service Learning Built in a Lecture-Based Aging Course? Paper presented at Grand Valley State University Student Scholars Day, virtual.

Hart, L. (2020) Mindfulness Meditation Effect on Life Satisfaction and Self-Esteem in Retirement Home Residents. Poster presented at the Art and Science of Aging Conference.

Hart, L., Montalbano, J., Warner, A., & Zanders, S. (2019) The Effect of Different Pre-exercise Treatments on Power Output. Poster presented at Grand Valley State University Student Scholars Day.

**PROFESSIONAL AFFILIATIONS**

2022-Present Student member, Society for Text and Discourse

2022-Present Student member, Psychonomic Society

2022-Present Student member, Midwestern Psychological Association

2019-Present Member, Psi Chi

**COURSES**

**Psychology** SWS Research Methods in Psychology (PSY 300) • Child Development (PSY 301) • Psychopathology (PSY 303) • Foundations of Neuroscience (PSY 330) • Psychology of Language (PSY 357) • Social Psychology (PSY 360) • Cognition (PSY 365) • Perspectives on Aging (PSY 366) • Cognitive Neuroscience (PSY 370) • Advanced Research Methods in Psychology (PSY 400) • Advanced General: The Capstone (PSY 492) • Independent Study and Research (PSY 499)

**Statistics** Intermediate Applied Statistics (STA 216) • Design of Experiments (STA 315) • Statistical Computing (STA 318) • Applied Regression Analysis (STA 321) • Statistical Computing and Graphics with R (STA 418) • Multivariate Data Analysis (STA 426)

**Philosophy** Philosophy of Mind (PHI 430)

**REFERENCES**

**Michael Wolfe**

Grand Valley State University

1 Campus Drive, Allendale, MI

\(616\) 331-2989

<wolfem@gvsu.edu>

Relationship: Served as research assistant to Dr. Wolfe

**Todd Williams**

Grand Valley State University

1 Campus Drive, Allendale, MI

\(616\) 331-8976

<willitod@gvsu.edu>

Relationship: Served as research assistant to Dr. Williams

**Jing Chen**

Grand Valley State University

1 Campus Drive, Allendale, MI

\(616\) 331-2867

<chenj@gvsu.edu>

Relationship: Served as research assistant to Dr. Chen