---
title: "Proposed Study (Discontinued because of COVID-19): Examining the Effect of Mindfulness Meditation on Life Satisfaction and Self-Esteem in Retirement Home Residents"
preview: "senior-yoga-meditation.jpeg"
date: 2020-02-26
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

I gave a talk at the 15th annual Art & Sciences of Aging (2020). I propose a study to examine the effect of mindfulness meditation on the life satisfaction and self-esteem of retirement home resident. Unfortunately, this study never saw the light of day. Just a few days before I began to collect data for this study, the COVID-19 pandemic had put an end to in-person research for the foreseeable future.

## Abstract

Mindfulness can be used to describe a variety of practices and processes that generally involves focusing on the present moment and being conscious and aware. Mindfulness meditation has been shown to decrease stress, anxiety, and depression, so it is likely that it will increase life satisfaction and self-esteem. In this poster, I will propose a study that seeks to determine the effect of mindfulness meditation on life satisfaction and self-esteem in older adults living in retirement homes. Participants will undergo an 8-week mindfulness meditation intervention, following a 10-minute guided meditation 4 times per week and will be encouraged to practice daily. Life satisfaction and self-esteem will be measured before and after the 8-week mindfulness meditation.

## Talk

```{r}
vembedr::embed_youtube("UQbXFcVv8iw")
```

