---
title: "Can Ageism Be Reduced by Service Learning Built in a Lecture-Based Aging Course?"
preview: "ageism_img.jpeg"
date: 2021-04-13
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

I gave a talk at the 25th annual Student Scholars Day at Grand Valley State University in Allendale, Michigan. I present preliminary evidence on an ongoing study that found a significant decrease in ageism in college students following a lecture-based psychology course on aging that included a service-learning project.

## Abstract

Ageism, or prejudicial attitudes about individuals based on age, is pervasive in society. Theories such as terror management theory, social identity theory, and stereotype embodiment theory have been used to explain what may give rise to ageism. Research also suggests that education about aging and reciprocal intergenerational interactions can reduce ageism and a combination of these two could be most effective. The present study investigated whether college student’s perception of old age can be influenced by taking a psychology class on aging, a lecture and discussion-based course with a project that requires students to participate in activities with residents at a local retirement home. The Fraboni Scale of Ageism (FSA) was administered to the students at the beginning and end of the course. The results showed a significant reduction in the overall score and two out of three subscales of FSA (stereotype and separation but not affective attitudes).

## Talk

```{r}
vembedr::embed_youtube("q2vcf8vAUoY")
```



