---
title: "Belief Change Predicts Argumentative Essay Content After Reading"
preview: "arg_essay.jpeg"
date: 2022-07-22
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

I gave an enhanced presentation at the 2022 Society for Text and Discourse Conference. which was virtual. I present data on how belief change may influence the components included in an argumentative essay.

## Abstract

Believers and disbelievers in gun control effectiveness wrote a 250 word essay explaining their beliefs after reading a one-sided text that was either consistent or inconsistent with their beliefs. Essays were coded for number of reasons and the presence or absence of a claim, counterargument, text content, policy claim, metacognitive statement, and evaluative statement about the text. Between group differences in essay characteristics and how they relate as a function of belief change are discussed.

## Talk

```{r}
vembedr::embed_youtube("a1Pu7sliKxA")
```


